---
title: "get_literature_by_country"
author: "João Vitor"
date: "10/06/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Paper data acquisition

Loading necessary packages

```{r}
library(tidyverse)
library(rvest)
library(httr)
```

This functions acquires papers from a selected country

```{r get-country-papers}
get_country_papers <- function(country) {
  url <- paste0('https://www.ncbi.nlm.nih.gov/research/coronavirus-api/export/tsv?filters=%7B%22countries%22%3A%5B%22', 
                country,
                '%22%5D%7D')
  
  read_tsv(url, skip = 31) %>% 
    mutate(paper_link = paste0("https://pubmed.ncbi.nlm.nih.gov/", pmid))
}
```

This one gets the paper's abstracts from pubmed, use this with care, since
pubmed has, justifiably, strict rate limiting. I've commented out a get-around using sys.sleep
that is necessary for larger queries.

```{r get_paper_abstract}
get_paper_abstract <- function(link) {
  
  message(paste("Current abstract:",link))
  
  read_html(link) %>% 
    html_nodes(css = "#en-abstract > p:nth-child(1)") %>% 
    html_text() %>% 
    str_trim()
  
  #Sys.sleep(20)
}
```

This gets the doi using entrez.

```{r}
get_doi_from_pmid <- function(pmid) {

  pmid <- as.character(pmid)
  
  url <- paste0("https://eutils.ncbi.nlm.nih.gov/entrez/eutils/esummary.fcgi?db=pubmed&id=",
                pmid,
                "&retmode=json")
  
  jsonlite::fromJSON(url)$result %>% 
    '[['(pmid) %>% 
    '[['('articleids') %>% 
    filter(idtype == 'doi') %>% 
    pull(value)
}
```

Let's take a look at Brazil first.

```{r}
br <- get_country_papers('Brazil') %>% 
  mutate(abstract = map(paper_link, possibly(get_paper_abstract, otherwise = NA)),
         doi = map_chr(pmid, possibly(get_doi_from_pmid, otherwise = NA)))
```


